---
title: "Basic Inferential Data Analysis"
author: "Hatem Jasim Hatem"
date: "May 13, 2019"
output: pdf_document
---
```{r}
library(ggplot2)
```
##1. Load the ToothGrowth data and perform some basic exploratory data analyses
```{r}
data(ToothGrowth)
str(ToothGrowth)
head(ToothGrowth)
tail(ToothGrowth)
```
##2. Provide a basic summary of the data.
```{r}
summary(ToothGrowth)

ggplot(aes(x=supp, y=len), data=ToothGrowth) + geom_boxplot(aes(fill=supp))+ 
        labs(x="Supplement", y= "Tooth length")
```

## 3. Use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose.
```{r}


# Convert dose to a factor
ToothGrowth$dose<-as.factor(ToothGrowth$dose)

# Plot tooth length vs. the dose amount, broken out by supplement 
ggplot(aes(x=dose, y=len), data=ToothGrowth) + 
  geom_boxplot(aes(fill=dose))+ 
  facet_grid(~ supp)+
  labs(x = "Dose Amount", y = "Tooth Length")
```
The figure show there are different in tooth growth. To determine the difference is significante or not used t-test

```{r}
ToothGrowth_sub <- subset(ToothGrowth, ToothGrowth$dose %in% c(1.0,0.5))
# T-test for vitamine c when dose 1 or 0.5 mg
t.test(len ~ dose, ToothGrowth_sub[ToothGrowth_sub$supp =='VC', ])$p.value
# T-test for orange juice when dose 1 or 0.5 mg
t.test(len ~ dose, ToothGrowth_sub[ToothGrowth_sub$supp =='OJ', ])$p.value
ToothGrowth_sub <- subset(ToothGrowth, ToothGrowth$dose %in% c(2.0, 1.0))
# T-test for vitamine c when dose 2 or 1 mg
t.test(len ~ dose, ToothGrowth_sub[ToothGrowth_sub$supp =='VC', ])$p.value
# T-test for orange juice when dose 2 or 1 mg
t.test(len ~ dose, ToothGrowth_sub[ToothGrowth_sub$supp =='OJ', ])$p.value
```

```{r}
# Plot tooth length vs. supplement  method broken out by the dose 
ggplot(aes(x=supp, y=len), data=ToothGrowth) + 
  geom_boxplot(aes(fill=supp))+ 
  facet_grid(~ dose) + 
  labs(x = "Supplement", y = "Tooth Length")
```
The figure show there are different in tooth growth. To determine the difference is significante or not used t-test

```{r}
# T-test for supplement when dose 0.5 mg
t.test(len ~ supp, ToothGrowth[ToothGrowth$dose == .5, ])$p.value

# T-test for supplement when dose 1 mg
t.test(len ~ supp, ToothGrowth[ToothGrowth$dose == 1, ])$p.value

# T-test for supplement when dose 2 mg
t.test(len ~ supp, ToothGrowth[ToothGrowth$dose == 2, ])$p.value
```
## 4. State your conclusions and the assumptions needed for your conclusions.

Because the alternative hypothesis $H_a$ is cost and may be dangerous therefore set alpha to 0.01 $\alpha = 0.01$. 
According to p-value of T-test the orange juice (OJ) more effective on tooth growth than vitamine c (VC) when dose is 0.5 or 1 mg but simlar effective in vitamine c when dose 2 mg