---
title: "Simulation Exercise"
author: "Hatem Jasim Hatem"
date: "May 13, 2019"
output: pdf_document
---
```{r }
library(ggplot2)
```

#Part 1: Simulation Exercise Instructions
In this project you will investigate the exponential distribution in R and compare it with the Central Limit Theorem. The exponential distribution can be simulated in R with rexp(n, lambda) where lambda is the rate parameter. The mean of exponential distribution is 1/lambda and the standard deviation is also 1/lambda. Set lambda = 0.2 for all of the simulations. You will investigate the distribution of averages of 40 exponentials. Note that you will need to do a thousand simulations.

##1. Show the sample mean and compare it to the theoretical mean of the distribution.


```{r}
n <- 40
Lambda <- 0.2
mns = NULL
for (i in 1 : 1000) mns = c(mns, mean(rexp(n, Lambda)))
SampleMean<- mean(mns)
TheoreticalMean <- 1/Lambda
paste('Sample Mean', SampleMean, 'Theoretical Mean', TheoreticalMean, sep = ': ')
```
***Sample mean `r SampleMean` approximately equal to theoretical mean `r TheoreticalMean`***

```{r}
hist(mns, xlab = "Mean", 
     main="Distribution of Exponential Mean")
abline(v = TheoreticalMean, col="red")
abline(v = SampleMean, col="blue")
legend("topright",c("Theoretical Mean", "Simulation Mean"),
       cex=.8,col=c("red","blue"), pch=c('|','|'))
```

##2. Show how variable the sample is (via variance) and compare it to the theoretical variance of the distribution.


```{r}
# sample deviation & variance form sample 
sample_std <- sd(mns)
sample_variance <- sample_std^2
paste('sample stander deviation', sample_std, 'sample variance', 
      sample_variance, sep = ': ')
```
Sample stander deviation can calculated theoretically accourding to  this formula: $S = \frac{\sigma}{\sqrt{n}}$ and sample variance accourding to this formula $variance= S^2$
```{r}
# theoretical deviation & variance form pupluation parapeter 
theoretical_std <- (1/Lambda)/sqrt(n)
theoretical_variance  <- theoretical_std^2
paste('Theoretical stander deviation', theoretical_std, 
      'Theoretical variance', theoretical_variance, sep = ': ')
```

***The simulation variance `r sample_variance` approximately equal to Theoretical variance `r theoretical_variance`***

##3. Show that the distribution is approximately normal.



```{r}

ds <- data.frame(mns)
ggplot(ds, aes(x = mns)) +
 geom_histogram(binwidth = .2, color="black", fill="gray" , aes(y=..density..))+
            stat_function(fun=dnorm, args=list(mean=TheoreticalMean, sd=sd(mns)), 
                          color="green", size =1) +
            stat_density(geom = "line", color = "red", size =1)  +
            labs(x="Mean", y= "Density")
```
***The above figure show that sample distribution curve is approximately similar to normal distribution curve.***

For further explaint used Q-Q Normal Plot to compare between sample quantiles and theortical quantiles 
```{r}
qqnorm(mns, col = 'red')
qqline(mns, col = "green")
```
